Energy and the CES production function

### 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
plots for resamples;

<<>>=
OEplot <- function( data ) {
  ggplot( data %>% 
          mutate(
            slice = interaction(Country, flavor, lex.order=TRUE, sep= " ")
            )
          ) +
    tri_theme() +
    tri_grid() +
    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
    geom_tripath( 
      aes(x=oe1, y=oe2, z=oe3, 
          colour = Year,
          group=interaction(Country, nest, flavor)),
      alpha=0.6,  size=1) +
    geom_tripoint( 
      aes(x=oe1, y=oe2, z=oe3, colour = Year, size=Year), 
      alpha=0.7, shape=21)  +
    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
    facet_grid(nest ~ slice) +
    scale_size_continuous( range = c(1.4, 4))
}
OEplot(AllOE) 
@

@@

>>>>

<<>>=
OEplot <- function( data ) {
  ggplot( data %>% 
          mutate(
            slice = interaction(Country, flavor, lex.order=TRUE, sep= " ")
            )
          ) +
    tri_theme() +
    tri_grid() +
    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
    geom_tripath( 
      aes(x=oe1, y=oe2, z=oe3, 
          colour = Year,
          group=interaction(Country, nest, flavor)),
      alpha=0.6,  size=1) +
    geom_tripoint( 
      aes(x=oe1, y=oe2, z=oe3, colour = Year, size=Year), 
      alpha=0.7, shape=21)  +
    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
    facet_grid(nest ~ slice) +
    scale_size_continuous( range = c(1.4, 4))
}

OEplot2 <- function( data ) {
  ggplot( data %>% 
          mutate(
            slice = interaction(Country, flavor, lex.order=TRUE, sep= " ")
            )
          ) +
    tri_theme() +
    tri_grid() +
    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
    geom_tripath( 
      aes(x=oe1, y=oe2, z=oe3, 
          colour = Year,
          group=interaction(Country, nest, flavor)),
      alpha=0.6,  size=1) +
    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
    facet_grid(nest ~ slice) +
    scale_size_continuous( range = c(1.4, 4))
}
OEplot(AllOE) 
OEplot2(AllOE) 
@

@@

<<>>=
ReModels <-
  bind_rows(
  leaf_apply(resampleModels, 
             function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
             strict.lists = TRUE)
)

OEplot(ReModels)
OEplot2(ReModels)
@

<<>>=
ReModels %>% 
  gather(factor, elasticity, oe1, oe2, oe3) %>%
  ggplot(aes(x=Year)) + 
  geom_line( 
    aes(y = elasticity,
        alpha = grepl("orig", id),
        group = interaction(id, factor),
        color = factor,
        linetype = factor,
        size = grepl("orig", id)
    ) ) +
  facet_grid(. ~ Country) +
  scale_alpha_manual(
    name = "",
    values = c(.3, 1),
    guide = FALSE
  ) + 
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70"),
    guid=FALSE
  ) +
  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(.3, .9),
    guide = FALSE) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1) ) + 
  xy_theme() +
  labs(x="", y="")
